Title of the paper

### 2022-06-09 Manuscript/src/sections/titleAbstract.tex
paper: updated abstract

\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:
\author{Elsevier\fnref{myfootnote}}
\address{Radarweg 29, Amsterdam}
\fntext[myfootnote]{Since 1880.}

%% or include affiliations in footnotes:
\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
\ead[url]{www.elsevier.com}

\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{support@elsevier.com}

\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
\address[mysecondaryaddress]{360 Park Avenue South, New York}

@@

\begin{keyword}
\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
\MSC[2010] 00-01\sep  99-00
\end{keyword}

>>>>

    \title{Title of the paper}

    \author[label1]{Federico Tartarini\corref{mycorrespondingauthor}}
    \ead{federicotartarini@berkeley.edu}
    \author[label2]{Stefano Schiavon}

    \address[label1]{Berkeley Education Alliance for Research in Singapore, Singapore}
    \address[label2]{Center for the Built Environment, University of California, Berkeley, CA, USA}

    \cortext[mycorrespondingauthor]{Corresponding author}

@@

    \begin{keyword}
        Personal thermal comfort model \sep Ecological momentary assessment \sep Skin temperature \sep Machine learning \sep Internet of Things (IoT)
    \end{keyword}
